ScipionBox: automatic processing for

### 2017-06-07 2.overall.tex
Updates from ShareLaTeX

In most cases, after importing data, the first step will be to correct for beam-induced movement. For this task, \scipionbox allows you to choose between five different algorithms from three different labs (an exhaustive list containing the approximately 150 algorithms available in \scipionbox is at appendix XX). This multiplicity of possibilities is available at each different processing step although, if found overwhelming, may be ignored by choosing one of the default prepacked workflows.

@@

Another set of  specialized protocols are grouped under the name ``consensus''. For a given logical step (for example, particle picking) these protocols check if the datasets obtained from the same input data using different algorithm are identical. Continuing with the particle picking example, ``consensus picking'' will compare the particles selected for each one of the executed algorithms and report on the particles selected by most of them.

\scipionbox is a streaming system that runs on threads. This is a significant difference from a script, since it means that each module is run independently. For example, Do you want to add a new protocol or monitor in your workflow while it is running? No problem, do it. \scipionbox allows workflows to be  modified on the fly. The modification will not interfere with the already executed steps and may take advantage from all already computed data. Did something go wrong and the microscope stopped? By default \scipionbox will stop after 2 hours with no microscope activity, but if you wish to continue your acquisition after a stop just press the continue button [*+ scipion 1.1.2], there is no need to restart from the beginning.

>>>>

In most cases, after importing data, the first step will be to correct for beam-induced movement. For this task, \scipionbox allows you to choose between five different algorithms from three different labs (an exhaustive list containing the approximately 150 algorithms available at [**ROB \url{XXXX}]). This multiplicity of possibilities is available at each different processing step although, if found overwhelming, may be ignored by choosing one of the default prepacked workflows.

@@

Another set of  specialized protocols are grouped under the name ``consensus''. For a given logical step (for example, particle picking) these protocols check if the datasets obtained from the same input data using different algorithm are consistent. Continuing with the particle picking example, ``consensus picking'' will compare the particles selected for each one of the executed algorithms and report on the particles selected by most of them.

\scipionbox is a streaming system that runs on threads. This is a significant difference from a script, since it means that each module is run independently. For example, Do you want to add a new protocol or monitor in your workflow while it is running? No problem, do it. \scipionbox allows users to modify  workflows on the fly without modifiying a single code line. The modification will not interfere with the already executed steps and may take advantage from all already computed data. Did something go wrong and the microscope stopped? By default \scipionbox will stop after 2 hours with no microscope activity, but if you wish to continue your acquisition after a stop just press the continue button [*+ scipion 1.1.2], there is no need to restart from the beginning.
